Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-04 paper/paper_new.tex
Updates from Overleaf

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}

@@

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use [apply] machine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual [*human] means. This paper reports on a research applying machine-driven [*automatic] approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network, and, further support empirical [*predicative] analysis [analytics?]. This paper reports specifically on research combining machine learning  and  image  informatics tools and techniques. A sample 7244 images from the Illinois Natural History Survey (INHS) were examined via automatic processes [*<--needs help]. Key findings indicate z, y, z.
%for x, y, z, can we give some numbers? thinking on this.
Results show we can  accurately extract metadata, such as, fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also indicate that automatic approaches "can outperform humans" [*and/or "expedite"] the creation of metadata that's critical to leveraging digitized specimens for machine learning. This research has implications for tens of thousands of digitized specimens stored in globally, accessible open repositories.
%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.

>>>>

\title{Automatic Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }}

@@

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source particularly for researchers seeking use apply achine learning to the vast collections of digitized specimens. Unfortunately, the metadata available is often sparse and, at times, erroneous; and it is prohibitively expensive to address these limitations through traditional, manual means. This paper reports on a research applying machine-driven approaches to analyze digitized fish images and extract a variety of important features. The digitized fish specimen are being analyzed as part of Biology Guided Neural Networks (BGNN) initiative, where researchers are developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. The automatically generated metadata is crucial for identifying high-quality images for the neural network to support predictive analyses.%predictive analytics?
Research combining machine learning  and  image  informatics tools and techniques allow us to rapidly enrich the metadata currently associated with the digitized specimens. The study focuses on a sample of 7244 images from the Illinois Natural History Survey (INHS), which also included additional, manually generated image-quality metadata Results show we can  accurately generate metadata for six key %6? 
metadata properties: fish quantity, fish orientation, image scaling based on ruler identification and measurement, and general image quality metrics. Results also show can also x, y, z.
%to confirm list
%jg to add note about x, y, z, unless someone else does first
The automatic process out-performs humans in terms and cost, and provides a solution for leveraging digitized specimens for machine learning. This research has implications for harnessing the tens of thousands of digitized specimens stored in globally, accessible open repositories.
%[another way to make this last sentence, so we can use the word novel?] the research presented here offers a novel approach for leveraging.
